MLISA: Machine Learning-based \\ Intelligent Service Agents (to change)

### 2014-09-29 papers/webservice-coalition-learning/webservice_coalition_learning.tex
changes

Let $P_{C_i}^t = \{C_1 >_{i}^t C_2 >_{i}^t .... >_{i}^t C_n\}$ be an ordered set of preferences for community $C_i$ at time $t$. Based on this ordered set, we define $K^t(C_i, k)$ as set of $k$ most preferred communities of community $i$ at time $t$.
%\subsubsection{feature vector generation}\label{sss:fvg}
\begin{equation}\label{h_t_pref_top}
\begin{split}				
K^t(C_i, k) = &\Big\{C_x | C_x >_{i}^t C_y; \forall C_y \in CFVS\ \\
				      &\wedge C_y \notin \{K^t(i, 1),K^t(i, 2),...,K^t(i, k-1)\} \Big\}				
\end{split}
\end{equation}
Based on $K^t(C_i, k)$ we define a set of communities for $C_i$ in which they are k most preferred communities for community $i$ and also community $i$ belongs to k most preferred communities of any of communities in set $K^t(C_i, k)$. This basically implies the preference is both sided.
\begin{equation}\label{l_t_top_both}
\begin{split}	
L^t(C_i,k) = &\Big\{C_j | C_j \in K^t(C_i, k) \\
             &\wedge C_i \in \{\bigcup_{C_x \in K^t(C_i, k)}K^t(C_x, k)\}\Big\}
\end{split}
\end{equation}
\subsection{Learning Model}\label{ss:learningmodel}

\subsubsection{training data set}\label{sss:tds}
\subsubsection{cross validation data set}\label{sss:cvds}
\subsubsection{sigmoid learned hypothesis function}\label{sss:slh}
\subsubsection{rationalized decision maker}\label{sss:rdm}

@@

>>>>

Let $P_{C_i}^t = \{C_1 >_{i}^t C_2 >_{i}^t .... >_{i}^t C_n\}$ be an ordered set of preferences for community $C_i$ at time $t$. Based on this ordered set, we define $K^t(C_i, k)$ as set of $k$ most preferred communities of community $i$ at time $t$.
%\subsubsection{feature vector generation}\label{sss:fvg}
\begin{equation}\label{h_t_pref_top}
\begin{split}				
K^t(C_i, k) = &\Big\{C_x | C_x >_{i}^t C_y; \forall C_y \in CFVS\ \\
				      &\wedge C_y \notin \{K^t(i, 1),K^t(i, 2),...,K^t(i, k-1)\} \Big\}				
\end{split}
\end{equation}
Based on $K^t(C_i, k)$ we define a set of communities for $C_i$ in which they are k most preferred communities for community $i$ and also community $i$ belongs to k most preferred communities of any of communities in set $K^t(C_i, k)$. This basically implies the preference is both sided.
\begin{equation}\label{l_t_top_both}
\begin{split}	
L^t(C_i,k) = &\Big\{C_j | C_j \in K^t(C_i, k) \\
             &\wedge C_i \in \bigcup_{C_x \in K^t(C_j, k)}K^t(C_x, k)\Big\}
\end{split}
\end{equation}

\subsection{Learning Model}\label{ss:learningmodel}

learning model text

@@

\begin{figure}%[!t]
\centering
\includegraphics[width=3.5in]{figures/utility_gain.eps}
\caption{Utility Gain}
\label{utility_gain1}
\end{figure}

line line line

\begin{figure}%[!t]
\centering
\includegraphics[width=3.5in]{figures/utility_gain_r.eps}
\caption{Utility Gain}
\label{utility_gain2}
\end{figure}

line line line

\begin{figure}%[!t]
\centering
\includegraphics[width=3.5in]{figures/utility_ratio.eps}
\caption{Utility Gain}
\label{utility_gain3}
\end{figure}

line line line

\begin{figure}%[!t]
\centering
\includegraphics[width=3.5in]{figures/utility_ratio_r.eps}
\caption{Utility Gain}
\label{utility_gain4}
\end{figure}

roc roc roc

\begin{figure}%[!t]
\centering
\includegraphics[width=3.5in]{figures/roc.eps}
\caption{RoC Curve}
\label{roc5}
\end{figure}

roc roc roc

\begin{figure}%[!t]
\centering
\includegraphics[width=3.5in]{figures/stats1.eps}
\caption{Overall Utility of all communities}
\label{stats1}
\end{figure}

roc roc roc

\begin{figure}%[!t]
\centering
\includegraphics[width=3.5in]{figures/stats2.eps}
\caption{Utility Gain on time}
\label{stats2}
\end{figure}

roc roc roc

\begin{figure}%[!t]
\centering
\includegraphics[width=3.5in]{figures/stats3.eps}
\caption{Average Community Size}
\label{stats3}
\end{figure}
